Coupling

### 2019-12-07 coupling.tex
pavel discuss

We have already seen that $S_{\rm BV}$ is consistent, so satisifies the ordinary classical master equation $\{S_{\rm BV}, S_{\rm BV}\}$. 
We decompose the remaining terms in the classical master equation \ref{CMEcouple} into components based on the cardinality of the number of odd supersymmetry inputs, many of which have already been studied in Sections \ref{sec: vector} and \ref{sec: hyper}. 
The new equations we must verify are the following:
\begin{equation}\label{CMEhyper2}
\begin{array}{rrrrrr}
\{S_{\rm BV} , I^{(1)}_{\rm couple}\} + \{I_{\rm couple}, I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}\} + \{I_{\rm couple}, I^{(1)}_{\rm couple}\} & = & 0 \\ 
\d_{CE} I^{(1)}_{\rm couple} + \{I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}, I^{(1)}_{\rm couple}\} + \frac{1}{2} \{I_{\rm couple}^{(1)}, I_{\rm couple}^{(1)}\} & = & 0 \\
\{I_{\rm couple}^{(1)}, I^{(2)}\} & =& 0 \\
%\{I^{(2)}, I^{(2)}\} & =& 0
\end{array}
\end{equation}

@@

\begin{lem} 
We have $\{I_{\rm couple}^{(1)}, I^{(2)}\} = 0$. 
\end{lem}
\begin{proof}
This follows from the simple observation that $I^{(2)}$ only involves the antifields $\lambda^*$, $\psi^*$ whereas $I^{(1)}_{\rm couple}$ only involves the fields $A$ and $\phi$.
So by type reasons, all terms in the bracket are zero.
\end{proof}

>>>>

We have already seen that $S_{\rm BV}$ is consistent, so satisifies the ordinary classical master equation $\{S_{\rm BV}, S_{\rm BV}\}$. 
We decompose the remaining terms in the classical master equation \ref{CMEcouple} into components based on the cardinality of the number of odd supersymmetry inputs, many of which have already been studied in Sections \ref{sec: vector} and \ref{sec: hyper}. 
The new equations we must verify are the following:
\begin{equation}\label{CMEcouple}
\begin{array}{rrrrrr}
\{S_{\rm BV} , I^{(1)}_{\rm couple}\} + \{I_{\rm couple}, I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}\} + \{I_{\rm couple}, I^{(1)}_{\rm couple}\} & = & 0 \\ 
\{I_{\rm couple}, I^{(2)}_{\rm gauge} + I^{(2)}_{\rm matter}\} + \d_{CE} I^{(1)}_{\rm couple} + \{I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}, I^{(1)}_{\rm couple}\} + \frac{1}{2} \{I_{\rm couple}^{(1)}, I_{\rm couple}^{(1)}\} & = & 0 \\
\{I_{\rm couple}^{(1)}, I^{(2)}\} & =& 0 \\
%\{I^{(2)}, I^{(2)}\} & =& 0
\end{array}
\end{equation}

The third equation is zero by type reasons.
\begin{lem} 
We have $\{I_{\rm couple}^{(1)}, I^{(2)}\} = 0$. 
\end{lem}
\begin{proof}
This follows from the simple observation that $I^{(2)}$ only involves the antifields $\lambda^*$, $\psi^*$ whereas $I^{(1)}_{\rm couple}$ only involves the fields $A$ and $\phi$.
So by type reasons, all terms in the bracket are zero.
\end{proof}

This leaves us to verify the first two equations of (\ref{CMEcouple}). 
We begin with the first equation.

@@

Finally, we verify the second equation in (\ref{CMEcouple}).

\begin{lem}
One has
\[
\{I_{\rm couple}, I^{(2)}_{\rm gauge} + I^{(2)}_{\rm matter}\} + \d_{CE} I^{(1)}_{\rm couple} + \{I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}, I^{(1)}_{\rm couple}\} + \frac{1}{2} \{I_{\rm couple}^{(1)}, I_{\rm couple}^{(1)}\} =  0.
\]
\end{lem}
\begin{proof}
The second and fourth terms are zero by type reasons.
Thus, we must show
\begin{equation}\label{CMEcouple2}
\{I_{\rm couple}, I^{(2)}_{\rm gauge} + I^{(2)}_{\rm matter}\} +  \{I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}, I^{(1)}_{\rm couple}\} = 0
\end{equation}

We begin by expanding $\{I_{\rm couple}, I^{(2)}_{\rm gauge}\}$:
\begin{align*}
\{I_{\rm couple}, I^{(2)}_{\rm gauge}\} (Q_1,Q_2) = & (\rho(\Gamma(Q_1,Q_2)) \lambda^*, \mu(\phi,\psi)) + (Q_1, \mu(\phi, \psi)) (Q_2, \lambda^*) + (Q_1, \lambda^*)(Q_2 \mu(\phi,\psi)) \\ + & (\psi^*, [i_{\Gamma(Q_1,Q_2)} A , \psi]) + (\phi^*, [i_{\Gamma(Q_1,Q_2)} A , \phi])
\end{align*}

Next, we expand $\{I_{\rm couple}, I^{(2)}_{\rm matter}\}$:
\begin{align*}
\{I_{\rm couple}, I^{(2)}_{\rm matter}\} = & (\rho(\Gamma(Q_1,Q_2)) \psi^*, [A, \psi]) + (\lambda, \mu(\phi, \rho(\Gamma(Q_1,Q_2)) \psi^*)) +  (\psi^*, [c, \rho(\Gamma(Q_1,Q_2)) \psi^*])
\end{align*}

Expanding $\{I^{(1)}_{\rm gauge}, I^{(1)}_{\rm couple}\}$:
\begin{align*}
\{I^{(1)}_{\rm gauge}, I^{(1)}_{\rm couple}\} = (\phi^* Q_1 , \rho([A,\phi]) Q_2) + \brian{finish}
\end{align*}

\end{proof}
